When Do You Repeat Yourself?\\ Voices from the Trenches of Linux Kernel Maintainers on Code Duplication

### 2025-10-29 papers/techdebt2026/techdebt.tex
techdebt2026: techdebt: update Zenodo link to replication package v2
Given that we updated the replication package with Luan's threads,
update the link in the paper.

Signed-off-by: David Tadokoro <davidbtadokoro@usp.br>

All anonymized threads containing the entire review process and interactions with maintainers are available in this Zenodo repository: \href{https://doi.org/10.5281/zenodo.17432193}{https://doi.org/10.5281/zenodo.17432193}.

>>>>

All anonymized threads containing the entire review process and interactions with maintainers are available in this Zenodo repository: \href{https://doi.org/10.5281/zenodo.17474124}{https://doi.org/10.5281/zenodo.17474124}.
